Grade Retention and Mixed Race

### 2022-08-19 products/paper/main.qmd
Add outline for rest of selection section

>>>>

1. its complicated
2. Rather than sort out a priori predictions, its important to control for most likely selected characteristics. In the case I explore here socioeconomic status and traits measuring assimilation such as foreign-born status and english language proficiency. 
3. This is not a "race vs. class" argument that diminishes the importance of race. Rather it delineates where generationally and by what mechanisms race might matter for biracial individuals.
